\chapter{Background}

\section{CESAR: Project Structure}
The CESAR project is a collaberation between the Univeristy of Oslo and Oslo Universitetssykehus, with a goal to reduce the the threshold to perform a clinical diagnosis of Obstructive Sleep Apnea (OSA) and to reduce the time to diagonize the disorder. Obstructive Sleep Apnea is a common sleeping disorder which affects the natural breathing cycle by reducing respiration or all airflow. As a consequence, OSA can lead to serious health implications, and in some cases, death through suffocation \cite{cesarinfo}. 

The CESAR project aim to use low cost sensor kit to prototype applications using physiological signals related to heart rate, brain activity, oxygen level in blood to monitor sleep and breathing related illnesses (e.g., Obstructive Sleep Apnea). As of now, the development in the project facilities for data acqusistion from various sensor sources and delegation of the data to subscribed applications. The Section X and Section X is a summary of the development and results of the development, and Figure X is an illustration of the projects development pipeline. 

Moving on, the previous work has incorporated support for a few sensor sources (i.e., Bitalino) in order to collect physiological signals. With the support for more sensor sources enables more precise detection and analysis of the disorder can be made. In Section X, a new sensor source is introduced. 

\input{sections/background/projectarchitecture.tex}

\section{Android OS}
\input{sections/background/android.tex}
