\subsection{Stakeholders}
A stakeholder is a term coined to describe those persons or organizations that have, or claim an interest in the project [Stakeholder defined, p. 4].  Identifying stakeholders is essential to fulfilling the requirement set in the thesis, as they contribute to form and sculpture the application. From the article [stakeholder defined, p.14] we can distinguish stakeholders into four categories: 1) \textit{contributing (primary) stakeholders} are those that participate in developing and sustaining the project; 2) \textit{observer (secondary) stakeholder} are those who affect or influence the project;  3) \textit{end-user (tertiary stakeholder)} is the one who interact and uses the output of the application; and 4) \textit{invested stakeholder} is one who has control of the project  [stakeholder defined, p. 13]. In Nidra, we have three stakeholders who affect the application, and each can be categorized respectfully.
\begin{itemize}
    \item \textbf{Patients} - are identified as an end-user; they interact with the application.  
    \item \textbf{Researchers/Doctors} - are identified as an observer stakeholder; they might not use the application itself. However, they might use the data obtained from the patients' recordings for further analysis. Additionally, request functionality in the application.
    \item \textbf{Developers} - are identified as a contributor stakeholder; they maintain the application from bugs or extend the functionally of the application. Additionally, they can contribute to developing modules that extend the functionality of the application. 
\end{itemize}
