\chapter{Introduction}\label{introduction}

\input{sections/introduction/motivation.tex}
\input{sections/introduction/problem.tex}

\section{Limitations}
Based on the goals and requirements stated in previous section, the scope of this thesis is to design and implement an application capable of recording breathing data obtained by the Flow sensor kit over an extended period. 

We limite the scope to integrating the support for the Flow sensor kit in Nidra, and exluded to test for already integrated sensor sources (e.g., Bitalino). Further, with the Flow sensor kit provided under development, we restricted the design to collect respiration (breathing) data (opposed to hearth-rate or other physiological data).

The application is designed to collect breathing data; we do not perform any analysis to predict or detect sleeping disorders based on the data. However, we facilitate for future developers to utilize the data provided by Nidra to perform such task.

Finally, the implementation is Android specific as the previous work performed on the project is designed soley for Android applications. 

\section{Research Method}
The work in this thesis can be classified as \textit{computing research} with a principle approach of an \textit{engineering method} as described in \cite{Glass_1995}. The engineering method (evolutionary paradigm) is to: (i) observe existing methods, (ii) propose a better solution, (iii)  build or develop artifacts\footnote{human-manufactured objects produced during the development}, and (iv) measure and analyze until no further improvements are possible. The report identifies patterns amongst various principle approaches and categorizes the the pattern into phases: \textit{(i) informational phase}, \textit{(ii) propositional phase}, \textit{(iii) analytical phase}, and \textit{(iv) evaluation phase}. Below, we give a brief description of each phase and discuss how our work fits into each of them. 

\subsection{Informational Phase}
The informational phase according to the report is to \textit{"gather or aggregate information via reflection, literature survey, people/organization survey, or poll"}

In this thesis, we survey previous related work in the field of detecting, analyzing, and diagnosing sleep related-breathing disorders on a mobile device. A vast amount of the work, use various techniques and methods to improve the diagnosis of the disorders (e.g., using the microphone and the accelerometer in the mobile device). Conclusively, they create an application from scratch, which is a time-consuming procedure.  In the motivation of this thesis, we focus on designing and implementing an application that allows future developers to extend or enrich the data in our application. As such, we expedite the creation of a mobile application, which allows future developers to leverage the functionality we provide to provide novelty in the research and study of sleep-related breathing disorders.

\subsection{Propositional Phase}
The propositional phase according to the report is to \textit{"propose and/or formulate a hypothesis, method or algorithm, model, theory, or solution"}

The solution proposition in this thesis is to create an application which will be used to record, share, and analyze breathing data collected over an extended period. We want to extend the CESAR project by providing an user-interface to the patient to perform these tasks while using the tools that the project facilitates. Mainly, we want to use the data stream dispatching tool will in order to manage current and future sensor sources. In which, we proceed to add support for the Flow sensor kit. In the end, we wish to facilitate an application that is used by the patients to record their breathing data during sleep and to share the data between researchers/doctors. As such, we aid in analyzing the data to detect sleep-related breathing disorders (e.g., obstructive sleep apnea) from home. 

\subsection{Analytical Phase}
The analytical phase according to the report is to \textit{"analyze and explore a proposition, leading to a demonstration and/or formulation of a principle or theory"}

With the proposition of this thesis, we analyze the tasks and separate them into concerns. Each concern has design choices that combined fulfills the goals of this thesis. As a demonstration, we realize the design choices by implementing them as an Android application, called Nidra. 

\subsection{Evaluation Phase}
The evaluation phase according to the report is to \textit{"evaluate a proposition or analytic finding by means of experimentation (controlled) or observation (uncontrolled, such as a case study or protocol analysis), perhaps leading to a substantiated model, principle, or theory"}

Based on the requirements and goal of this thesis, we evaluate the application by conducting experiments. The experiments include participants in order to test the application in the hands of human beings without prior knowledge of the application. In the end, evaluation and conclude whether the goals and requirements of this thesis are sufficient.

\section{Contributions}
Over the course of this thesis, we design and implemented an application for collecting, sharing, and analyzing breathing data. Also, we provided an extensible solution for modules to enrich the applications. The application is focused on creating a generalized application which manges sensor data with focus on sleep apnea / collecting data during sleep over an extended period, which purpose was to enable analyzing and sharing of the data with researchers/doctors. As defined in our problem statement, we set three research goals on the basis of three system requirements. Below, we present the goals and requirements and describe how our system meets them:

\begin{description}
    \item[Requirement 1] \textit{The application should provide an interface for the patient to 1) record physiological signals (e.g., during sleep); 2) present the results; and 3) share the results.}
    \item[Requirement 2] \textit{The application should ensure a seamless and continuous data stream, uninterrupted from sensor disconnections and human disruptions.}
    \item[Requirement 3] \textit{The application should provide an interface for the developers to create modules to enrich the data from records or extend the functionality of the application.}
\end{description}

With the requirements fulfilled, we can look at how Nidra solves our three research goals.

\begin{description}
    \item[Goal 1] \textit{Integrate the support for Flow sensor kit with the extensible data stream dispatching tool}
    \item[Goal 2] \textit{Research and develop a user-friendly application which facilitates collection of breathing data with the use of the extensible data stream dispatching tool.}
    \item[Goal 3] \textit{Create an extensible solution such that the developers can integrate stand-alone applications in our application.}
\end{description}



\section{Thesis Outline}
The thesis is divided into three parts, which the following list presents a general overview of:

\begin{itemize}
    \item Part 1: \textbf{Introduction \& Background}
    \begin{description}[font=\normalfont\itshape]
        \item[Chapther 2: Background] presents the background material necessary for understanding the fundamentals in this thesis. It starts by introducing the CESAR project and the tools provided for data acquisition. Then, an overview of the Android operating system architecture and components are 
        \item[Chapther 3: Related Work] presents the related work focusing on creating a mobile applicaton to collect physiological data in order to diagnose sleep apnea. Finally, we discuss why our solution is an improvement to the related work.
    \end{description}

    \item Part 2: \textbf{Design \& Implementation}
    \begin{description}[font=\normalfont\itshape]
        \item[Chapther 4: Analysis and High-Level Design] encompasses the functional requirements, the design purposal, and the structure of the data in the application.
        \item[Chapther 5: Implementation] realizes the design purposal in Android, with the use of the previous work.
    \end{description}

    \item Part 3: \textbf{Evaluation \& Conclusion}
    
    \begin{description}[font=\normalfont\itshape]
        \item[Chapther 6: Evaluation] conducts various experiements in order to tests if the system requirements is fullfilling.
        \item[Chapther 7: Conclusion] discuss the objectives and the overall goal of the thesis, with suggestions to future work.
    \end{description}

\end{itemize}

